Visual proteomics using whole-lamella 2D template matching

### 2022-02-21 manuscript.tex
Merge pull request #1 from jojoelfe/rootstock-2022-02-21 [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/fd67573aae85b96b8a70c12b88d9cb7dbe226559.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/fd67573aae85b96b8a70c12b88d9cb7dbe226559/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1876510914

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/a8f7e15ca68cda59eec8dcd51b56efdb54e9344e/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/a8f7e15ca68cda59eec8dcd51b56efdb54e9344e}{jojoelfe/deco\_lace\_template\_matching\_manuscript@a8f7e15}
on February 20, 2022.

@@

\leavevmode\vadjust pre{\hypertarget{ref-VBmW7Aot}{}}%
\CSLLeftMargin{2. }
\CSLRightInline{\textbf{Fluorescence microscopy}
\CSLBlock{Jeff W Lichtman, José-Angel Conchello} \emph{Nature Methods} (2005-12) \url{https://doi.org/bbpg4n}
\CSLBlock{DOI: \href{https://doi.org/10.1038/nmeth817}{10.1038/nmeth817} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/16299476}{16299476}}}

\leavevmode\vadjust pre{\hypertarget{ref-tGQ6TSUo}{}}%
\CSLLeftMargin{3. }
\CSLRightInline{\textbf{A visual approach to proteomics}
\CSLBlock{Stephan Nickell, Christine Kofler, Andrew P Leis, Wolfgang Baumeister} \emph{Nature Reviews Molecular Cell Biology} (2006-03) \url{https://doi.org/d6d5mq}
\CSLBlock{DOI: \href{https://doi.org/10.1038/nrm1861}{10.1038/nrm1861} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/16482091}{16482091}}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Rksh2dxu}{}}%
\CSLLeftMargin{6. }
\CSLRightInline{\textbf{Electron tomography of cells}
\CSLBlock{Lu Gan, Grant J Jensen} \emph{Quarterly Reviews of Biophysics} (2012-02) \url{https://doi.org/czj9hr}
\CSLBlock{DOI: \href{https://doi.org/10.1017/s0033583511000102}{10.1017/s0033583511000102} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/22082691}{22082691}}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-18KGpXYPE}{}}%
\CSLLeftMargin{8. }
\CSLRightInline{\textbf{Label-free single-instance protein detection in vitrified cells}
\CSLBlock{JPeter Rickgauer, Heejun Choi, Jennifer Lippincott-Schwartz, Winfried Denk} \emph{Biophysics} (2020-04-24) \url{https://doi.org/gpbjfd}
\CSLBlock{DOI: \href{https://doi.org/10.1101/2020.04.22.053868}{10.1101/2020.04.22.053868}}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-gRoY21jY}{}}%
\CSLLeftMargin{10. }
\CSLRightInline{\textbf{Hallmarks of ribosomopathies}
\CSLBlock{Kim R Kampen, Sergey O Sulima, Stijn Vereecke, Kim De~Keersmaecker} \emph{Nucleic Acids Research} (2020-02-20) \url{https://doi.org/gpbjfm}
\CSLBlock{DOI: \href{https://doi.org/10.1093/nar/gkz637}{10.1093/nar/gkz637} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/31350888}{31350888} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7026650}{PMC7026650}}}

\leavevmode\vadjust pre{\hypertarget{ref-KAJ7221k}{}}%
\CSLLeftMargin{11. }
\CSLRightInline{\textbf{Diagnostic and prognostic implications of ribosomal protein transcript expression patterns in human cancers}
\CSLBlock{James M Dolezal, Arie P Dash, Edward V Prochownik} \emph{BMC Cancer} (2018-12) \url{https://doi.org/gc87j9}
\CSLBlock{DOI: \href{https://doi.org/10.1186/s12885-018-4178-z}{10.1186/s12885-018-4178-z} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/29530001}{29530001} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5848553}{PMC5848553}}}

>>>>

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/fd67573aae85b96b8a70c12b88d9cb7dbe226559/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/fd67573aae85b96b8a70c12b88d9cb7dbe226559}{jojoelfe/deco\_lace\_template\_matching\_manuscript@fd67573}
on February 21, 2022.

@@

\leavevmode\vadjust pre{\hypertarget{ref-VBmW7Aot}{}}%
\CSLLeftMargin{2. }
\CSLRightInline{\textbf{Fluorescence microscopy}
\CSLBlock{Jeff W Lichtman, José-Angel Conchello} \emph{Nature Methods} (2005-11-18) \url{https://doi.org/bbpg4n}
\CSLBlock{DOI: \href{https://doi.org/10.1038/nmeth817}{10.1038/nmeth817} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/16299476}{16299476}}}

\leavevmode\vadjust pre{\hypertarget{ref-tGQ6TSUo}{}}%
\CSLLeftMargin{3. }
\CSLRightInline{\textbf{A visual approach to proteomics}
\CSLBlock{Stephan Nickell, Christine Kofler, Andrew P Leis, Wolfgang Baumeister} \emph{Nature Reviews Molecular Cell Biology} (2006-02-15) \url{https://doi.org/d6d5mq}
\CSLBlock{DOI: \href{https://doi.org/10.1038/nrm1861}{10.1038/nrm1861} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/16482091}{16482091}}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Rksh2dxu}{}}%
\CSLLeftMargin{6. }
\CSLRightInline{\textbf{Electron tomography of cells}
\CSLBlock{Lu Gan, Grant J Jensen} \emph{Quarterly Reviews of Biophysics} (2011-11-15) \url{https://doi.org/czj9hr}
\CSLBlock{DOI: \href{https://doi.org/10.1017/s0033583511000102}{10.1017/s0033583511000102} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/22082691}{22082691}}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-18KGpXYPE}{}}%
\CSLLeftMargin{8. }
\CSLRightInline{\textbf{Label-free single-instance protein detection in vitrified cells}
\CSLBlock{JPeter Rickgauer, Heejun Choi, Jennifer Lippincott-Schwartz, Winfried Denk} \emph{Cold Spring Harbor Laboratory} (2020-04-24) \url{https://doi.org/gpbjfd}
\CSLBlock{DOI: \href{https://doi.org/10.1101/2020.04.22.053868}{10.1101/2020.04.22.053868}}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-gRoY21jY}{}}%
\CSLLeftMargin{10. }
\CSLRightInline{\textbf{Hallmarks of ribosomopathies}
\CSLBlock{Kim R Kampen, Sergey O Sulima, Stijn Vereecke, Kim De~Keersmaecker} \emph{Nucleic Acids Research} (2019-07-27) \url{https://doi.org/gpbjfm}
\CSLBlock{DOI: \href{https://doi.org/10.1093/nar/gkz637}{10.1093/nar/gkz637} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/31350888}{31350888} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7026650}{PMC7026650}}}

\leavevmode\vadjust pre{\hypertarget{ref-KAJ7221k}{}}%
\CSLLeftMargin{11. }
\CSLRightInline{\textbf{Diagnostic and prognostic implications of ribosomal protein transcript expression patterns in human cancers}
\CSLBlock{James M Dolezal, Arie P Dash, Edward V Prochownik} \emph{BMC Cancer} (2018-03-12) \url{https://doi.org/gc87j9}
\CSLBlock{DOI: \href{https://doi.org/10.1186/s12885-018-4178-z}{10.1186/s12885-018-4178-z} · PMID: \href{https://www.ncbi.nlm.nih.gov/pubmed/29530001}{29530001} · PMCID: \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5848553}{PMC5848553}}}
